О множествах точек на плоскости с целочисленными расстояниями

### 2018-08-22 vmmsh-2018/BetterLinearBound.tex
[vmmsh] Terminology

\begin{lemma}
	\label{lemma_preliminary_size}
	Пусть $S$~--- система Эрдёша,
	$M_1, M_2, M_3, M_4 \in S$,
	$M_1 \neq M_2$, $M_3 \neq M_4$,
	интервалы $M_1 M_2$ и $M_3 M_4$ не пересекаются,
	$d = \operatorname{diam} S > 5$.
	Тогда $|S| \leq 4 \cdot |M_1 - M_2| \cdot |M_3 - M_4| + \frac{d-5}{2}$.
\end{lemma}

@@

\begin{lemma}
	Пусть $S$~--- система Эрдёша,
	$d = \operatorname{diam} S > 5$,
	$k \geq 2$,
	$m \geq 2$,
	$ |S| = (k-1)m^2 + 2$.

>>>>

\begin{lemma}
	\label{lemma_preliminary_size}
	Пусть $S\in\mathfrak{M}_n$,
	$M_1, M_2, M_3, M_4 \in S$,
	$M_1 \neq M_2$, $M_3 \neq M_4$,
	интервалы $M_1 M_2$ и $M_3 M_4$ не пересекаются,
	$d = \operatorname{diam} S > 5$.
	Тогда $|S| \leq 4 \cdot |M_1 - M_2| \cdot |M_3 - M_4| + \frac{d-5}{2}$.
\end{lemma}

@@

\begin{lemma}
	Пусть $S\in\mthfrak{M}_n$,
	$d = \operatorname{diam} S > 5$,
	$k \geq 2$,
	$m \geq 2$,
	$ |S| = (k-1)m^2 + 2$.
